General purpose gene annotation using deep learning

### 2019-12-20 paper/main.tex
stuff

\title[short Title]{General purpose gene annotation using deep learning}
\author[Sample \textit{et~al}.]{Felix Stiehler\,$^{\text{\sfb 1,}}$$^\dagger$, Alisandra Denton\,$^{\text{\sfb 1,}}$$^\dagger$\, Andreas Weber\,$^{\text{\sfb 1,}*}$}
\address{$^{\text{\sf 1}}$Institue for Plant Biochemistry, Heinrich-Heine-University, Dusseldorf, D-40225, Germany}

@@

\section{Approach}
We seek to show a path for improving on current HMM-based methods both in performance and in the ability to generalize. To accomplish this, we use deep neural networks, which have been shown to have the potential to be superior in flexibility and accuracy to traditional machine learning methods when detecting complex patterns in variety of fields. The genomic data was preprocessed with Geenuff \citealp{Denton19} abc

>>>>

\title[short Title]{General purpose gene annotation using deep learning}
\author[Sample \textit{et~al}.]{Felix Stiehler\,$^{\text{\sfb 1,}}$$^\dagger$, Alisandra Denton\,$^{\text{\sfb 1,}}$$^\dagger$\, Marvin Steinborn\,$^{\text{\sfb 1}}$, Andreas Weber\,$^{\text{\sfb 1,}*}$}
\address{$^{\text{\sf 1}}$Institue for Plant Biochemistry, Heinrich-Heine-University, Dusseldorf, D-40225, Germany}

@@

\section{Approach}
We seek to show a path for improving on current HMM-based methods both in performance and in the ability to generalize. To accomplish this, we use deep neural networks, which have been shown to have the potential to be superior in flexibility and accuracy to traditional machine learning methods when detecting complex patterns in variety of fields. Our model uses the raw genomic sequence as input and produces base pair wise predictions for the present gene annotation. The genomic data was preprocessed with Geenuff \citealp{Denton19}
